### 2020-06-26 Strings2020/strings2/strings2.tex
Clean up preambles, update templates

\newcommand{\oppower}[2]{\mop{{#1}^{#2}}\!}
\newcommand{\sqsinh}{\oppower{\sinh}{2}}
\newcommand{\sqcosh}{\oppower{\cosh}{2}}

\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}

@@

%{
%	\noindent\itshape%
%	本文约定：度规$\eta\sim\pqty{-,+,+,+}$, 指标$\mu,\nu,\dots = 0,1,2,3,\ i,j,\dots = 1,2,3$.
%}

@@

		Na\"ively, $\normorder{bc\,\pd c}_{\,(0)}$ is \textit{defined} as $b(0)\,c(z_1)\,\pd c(z_2)$ while $z_1,z_2\to 0$, with singular terms subtracted; however, different ways of taking the limit might lead to different results. For example, we can first take $z_1\to 0$ then $z_2\to 0$, or we can first take $z_1\to z_2$ then $z_2\to 0$. This two procedures will differ by $

@@

				\normorder{bc\,\pd c}_{\,(0)},

@@

		T^{bc}(z)\,\normorder{bc\,\pd c}_{\,(0)}

@@

		}_{(z)}\,\normorder{bc\,\pd c}_{\,(0)}\,,

@@

		\normorder{(\pd b)\,c}_{\,(z)}\,
		\normorder{bc\,\pd c}_{\,(0)}

@@

			}_{\,(0)}

@@

			}_{\,(0)} + \order{z}

@@

			}}_{\,(0)}\,, \notag\\[1ex]

@@

		\normorder{bc}_{\,(z)}\,
		\normorder{bc\,\pd c}_{\,(0)}

@@

		\normorder{bc\,\pd c}_{\,(0)}

@@

%	note that $b,c$ are primaries with weight $(2,0)$ and $(-1,0)$, hence $Tb,Tc$ OPEs take the standard form of a $T\cdot(\text{primary})$ OPE. We have:
%	\begin{equation}
%	\begin{aligned}
%		T^{bc}(z)\,\normorder{bc\,\pd c}_{\,(0)}
%		&\sim \pqty{
%				\frac{2}{z^2}\,
%					\normorder{bc\,\pd c}
%				+ \frac{1}{z}\,\normorder{
%					(\pd b)\,c\pd c
%				}
%			} \\
%		&\phantom{\sim \quad}
%			+ \pqty{
%				\frac{-1}{z^2}\,
%					\normorder{bc\,\pd c}
%				+ \frac{1}{z}\,\normorder{
%					b\,(\pd c)(\pd c)
%				}
%			} \\
%		&\phantom{\sim \quad}
%			+ \pqty{
%				\frac{-1}{z^2}\,
%					\normorder{bc\,\pd c}
%				+ \frac{1}{z}\,\normorder{
%					bc\,\pd^2 c
%				}
%			} \\
%		&\sim \frac{1}{z}\,\pd\,
%			\normorder{bc\,\pd c}
%		\sim \frac{1}{z}\,\pd\,\pqty{
%			j - cT^X
%		}_{(0)} \\
%		&\sim \frac{1}{z}\,\pd j(0)
%		- \frac{1}{z}\,c(0)\,\pd T^X(0)
%		- \frac{1}{z}\,T^X(0)\,\pd c(0),
%	\end{aligned}\\
%		T(z)\,j(0)
%		\sim \frac{D}{2z^4}\,c(0)
%			+ \frac{2}{z^2}\,T^X(0)\,c(0)
%			+ \frac{1}{z}\,\pqty{
%				\pd j(0)
%				- T^X(0)\,\pd c(0)
%			}
%	\end{equation}

	\item For $jj$ OPE, we have:
	\begin{gather}
		j = cT^X + j',\quad
		j' \equiv j^{bc}
			+ \frac{3}{2}\,\pd^2 c,\quad
		j^{bc}
		= \frac{1}{2}\normorder{cT^{bc}}
		= \normorder{bc\,\pd c}\,,\\[1ex]
%		
%		j = \frac{1}{2}\,cT^X
%			+ \frac{1}{2}\,\normorder{cT}
%			+ \frac{3}{2}\,\pd^2 c,\\
%
	\begin{aligned}
		j_z j_0
		&\sim \normorder{\Bqty{T^X_z T^X_0}\,c_z c_0}
			+ \normorder{\Bqty{c_z j'_0}\,T^X_z}
			+ \normorder{\Bqty{j'_z c_0}\,T^X_0}
			+ {j'_z j'_0} \\[.5ex]
		&\sim \normorder{\Bqty{T^X_z T^X_0}\,c_z c_0}
			+ \normorder{\Bqty{c_z j^{bc}_0}\,T^X_z}
			+ \normorder{\Bqty{j^{bc}_z c_0}\,T^X_0}
			+ {j'_z j'_0}\,,
	\end{aligned}
	\end{gather}
	From now on, for convenience and clarity, we will use subscripts to denote variable dependence: $c_z = c(z)$. Let's compute this term by term. We have:
	\begin{align}
		\normorder{\Bqty{T^X_z T^X_0}\,c_z c_0}
		&\sim \normorder{\pqty{
			\frac{D}{2z^4}
			+ \frac{2}{z^2}\,{T^X_0}
			+ \frac{1}{z}\,{\pd T^X_0}
		}\pqty{
			z\,\pd c_0
			+ \frac{z^2}{2}\,\pd^2 c_0
			+ \frac{z^3}{6}\,\pd^3 c_0
		} c_0} \notag\\
		&\sim -\pqty{
			\frac{D}{2z^3}\,c\,\pd c_0
			+ \frac{D}{4z^2}\,c\,\pd^2 c_0
			+ \frac{D}{12z}\,c\,\pd^3 c_0
			+ \frac{2}{z}\,\normorder{T^X c\,\pd c_0}
		}, 
		\label{eq:BRST_TTcc_OPE} \\[2ex]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		jc OPE ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		j^{bc}_z c_0
		&\sim \frac{1}{2}\,
			\normorder{cT^{bc}}_{\,z}\,c_0
		\sim \frac{1}{2}\,c_z \Bqty{
			\normorder{T^{bc}}_{\,z}\,c_0
		}
		\sim \frac{1}{2}\,c_z \Bqty{
			T_z\,c_0
		} \notag\\
		&\sim -\frac{1}{2}\,\pqty{
			\frac{-1}{z^2}\,c_0
			+ \frac{1}{z}\,\pd c_0
		}\pqty\big{
			c_0 + z\,\pd c_0
		} \sim 0, \\
		j^{bc}_0 c_z
		&\sim 0,
	\end{align}
	\begin{equation}
	\begin{aligned}
		j'_z j'_0
		&\sim j^{bc}_z j^{bc}_0
			+ \frac{3}{2}\,j^{bc}_z\,\pd^2 c_0
			+ \frac{3}{2}\,\pd^2 c_z\,j^{bc}_0 \\
		&\sim \frac{1}{2}\,
			\normorder{cT^{bc}}_{\,z}\,j^{bc}_0
		+ \frac{3}{2}\,\pqty{
			j^{bc}_z\,\pd^2 c_0
			+ \pd^2 c_z\,j^{bc}_0
		},
	\end{aligned}
	\end{equation}

@@

%	For the first term, we have:
%	\begin{equation}
%	\begin{aligned}
%		\normorder{cT^{bc}}_{\,z}\,j^{bc}_0
%		&\sim \normorder{\wick{
%			\c1 c T^{bc}_z \c1 j^{bc}_0
%		}} + \normorder{\wick{
%			c \c1 T^{bc}_z \c1 j^{bc}_0
%		}} + \normorder{\wick{
%			\bcontraction[1.1ex]{c}{T}{^{bc}_z}{j}
%			\c1 c T^{bc}_z \c1 j^{bc}_0
%		}} \\[.5ex]
%		&\sim \frac{1}{z}\,(+1)\,\normorder{
%			T^{bc}_z c\,\pd c_0
%		} + \normorder{c_z \Bqty{
%			\eqref{eq:BRST_Tj_OPE_partIII}
%		}} + \frac{1}{z}\,\normorder{\pqty\Big{
%			\Bqty{T^{bc}_z c_0}\,\pd c_0
%			+ (+1)\,
%				c_0\,\Bqty{T^{bc}_z\,\pd c_0}
%		}} \\
%		&\sim \frac{1}{z}\,\normorder{
%			T^{bc} c\,\pd c_0
%		} + \normorder{c_z \Bqty{
%			\eqref{eq:BRST_Tj_OPE_partIII}
%		}} + \frac{1}{z}\,\normorder{\pqty\Big{
%			\Bqty{T^{bc}_z c_0}\,\pd c_0
%			+ c_0\,\Bqty{T^{bc}_z\,\pd c_0}
%		}}
%	\end{aligned}
%	\end{equation}
%	Here we've used the fact that there is only one $b$ in $T^{bc}$, hence all non-singular are accounted for in the above expression. Note again that $c$ is primary; similar to \eqref{eq:BRST_Td2c_OPE}, we have:
%	\begin{equation}
%	\begin{aligned}
%		\normorder{cT^{bc}}_{\,z}\,j^{bc}_0
%		&\sim \normorder{\pqty{
%			c_0 + z\,\pd c_0
%			+ \frac{z^2}{2}\,\pd^2 c_0
%			+ \frac{z^3}{6}\,\pd^3 c_0
%		} \pqty{
%			\frac{-4}{z^4}\,c_0
%			+ \frac{3}{z^3}\,\pd c_0
%			+ \frac{1}{z^2}\,j^{bc}_0
%			+ \frac{1}{z}\,\pd j^{bc}_0,
%		}} \\
%		&\qquad + \frac{1}{z}\,\pqty{
%			\frac{-1}{z^2}\,c\,\pd c_0
%			+ c_0\cdot\frac{1}{z}\,\pd^2 c_0
%		} \\
%		&\sim \frac{3+4-1}{z^3}\,c\,\pd c_0
%			+ \frac{4/2+1}{z^2}\,c\,\pd^2 c_0
%			+ \frac{4/6}{z}\,c\,\pd^3 c_0 \\
%	\end{aligned}
%	\end{equation}
%	
%	
%	\begin{align}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%		ANOTHER OPE ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		j^{bc}_z\,\pd^2 c_0
%		&\sim \frac{1}{2}\,c_z\,\Bqty{
%			T^{bc}_z\,\pd^2 c_0
%		} \\
%		\sim\eqref{eq:BRST_Td2c_OPE}
%		&\sim \frac{1}{2}\,c_z\,\pqty{
%			\frac{-6}{z^4}\,c_0
%			+ \frac{-2}{z^3}\,\pd c_0
%			+ \frac{1}{z^2}\,\pd^2 c_0
%			+ \frac{1}{z}\,\pd^3 c_0
%		} \\
%		\sim (\textsl{Taylor})
%		&\sim \frac{1}{2}\,\pqty{
%			\frac{6-2}{z^3}\,
%				c_0\,\pd c_0
%			+ \frac{6/2+1}{z^2}\,
%				c_0\,\pd^2 c_0
%			+ \frac{6/6+1}{z}\,
%				c_0\,\pd^3 c_0
%		} \\
%		&\sim \frac{1}{2}\,\pqty{
%			\frac{4}{z^3}\,
%				c_0\,\pd c_0
%			+ \frac{4}{z^2}\,
%				c_0\,\pd^2 c_0
%			+ \frac{2}{z}\,
%				c_0\,\pd^3 c_0
%		} \\[2ex]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%		ANOTHER OPE ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		\pd^2 c_z\,j^{bc}_0
%		&\sim -j^{bc}_0\,\pd^2 c_z \\
%		&\sim - \frac{1}{2}\,c_0\,\Bqty{
%			T^{bc}_0\,\pd^2 c_z
%		} \\
%		\sim\eqref{eq:BRST_Td2c_OPE}
%		&\sim -\frac{1}{2}\,c_0\,\pqty{
%			\frac{-2}{(-z)^3}\,\pd c_z
%			+ \frac{1}{(-z)^2}\,\pd^2 c_z
%			+ \frac{1}{-z}\,\pd^3 c_z
%		} \\
%		&\sim -\frac{1}{2}\,c_0\,\pqty{
%			\frac{2}{z^3}\,\pd c_z
%			+ \frac{1}{z^2}\,\pd^2 c_z
%			+ \frac{-1}{z}\,\pd^3 c_z
%		} \\
%		\sim (\textsl{Taylor})
%		&\sim -\frac{1}{2}\,\pqty{
%			\frac{2}{z^3}\,c_0\,\pd c_0
%			+ \frac{1+2}{z^2}\,c_0\,\pd^2 c_0
%			+ \frac{-1+1+1}{z}\,c_0\,\pd^3 c_0
%		} \\
%		&\sim -\frac{1}{2}\,\pqty{
%			\frac{2}{z^3}\,c_0\,\pd c_0
%			+ \frac{3}{z^2}\,c_0\,\pd^2 c_0
%			+ \frac{1}{z}\,c_0\,\pd^3 c_0
%		} \\[1ex]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		\frac{3}{2}\,\pqty{
%			j^{bc}_z\,\pd^2 c_0
%			+ \pd^2 c_z\,j^{bc}_0
%		} &\sim \frac{3}{4}\,\pqty{
%			\frac{2}{z^3}\,c_0\,\pd c_0
%			+ \frac{1}{z^2}\,c_0\,\pd^2 c_0
%			+ \frac{1}{z}\,c_0\,\pd^3 c_0
%		}
%	\end{align}

>>>>

@@

@@

		Na\"ively, $\normorder{bc\,\pd c}_{(0)}$ is \textit{defined} as $b(0)\,c(z_1)\,\pd c(z_2)$ while $z_1,z_2\to 0$, with singular terms subtracted; however, different ways of taking the limit might lead to different results. For example, we can first take $z_1\to 0$ then $z_2\to 0$, or we can first take $z_1\to z_2$ then $z_2\to 0$. This two procedures will differ by $

@@

				\normorder{bc\,\pd c}_{(0)},

@@

		T^{bc}(z)\,\normorder{bc\,\pd c}_{(0)}

@@

		}_{(z)}\,\normorder{bc\,\pd c}_{(0)}\,,

@@

		\normorder{(\pd b)\,c}_{(z)}\,
		\normorder{bc\,\pd c}_{(0)}

@@

			}_{(0)}

@@

			}_{(0)} + \order{z}

@@

			}}_{(0)}\,, \notag\\[1ex]

@@

		\normorder{bc}_{(z)}\,
		\normorder{bc\,\pd c}_{(0)}

@@

		\normorder{bc\,\pd c}_{(0)}

@@

%	note that $b,c$ are primaries with weight $(2,0)$ and $(-1,0)$, hence $Tb,Tc$ OPEs take the standard form of a $T\cdot(\text{primary})$ OPE. We have:
%	\begin{equation}
%	\begin{aligned}
%		T^{bc}(z)\,\normorder{bc\,\pd c}_{(0)}
%		&\sim \pqty{
%				\frac{2}{z^2}\,
%					\normorder{bc\,\pd c}
%				+ \frac{1}{z}\,\normorder{
%					(\pd b)\,c\pd c
%				}
%			} \\
%		&\phantom{\sim \quad}
%			+ \pqty{
%				\frac{-1}{z^2}\,
%					\normorder{bc\,\pd c}
%				+ \frac{1}{z}\,\normorder{
%					b\,(\pd c)(\pd c)
%				}
%			} \\
%		&\phantom{\sim \quad}
%			+ \pqty{
%				\frac{-1}{z^2}\,
%					\normorder{bc\,\pd c}
%				+ \frac{1}{z}\,\normorder{
%					bc\,\pd^2 c
%				}
%			} \\
%		&\sim \frac{1}{z}\,\pd\,
%			\normorder{bc\,\pd c}
%		\sim \frac{1}{z}\,\pd\,\pqty{
%			j - cT^X
%		}_{(0)} \\
%		&\sim \frac{1}{z}\,\pd j(0)
%		- \frac{1}{z}\,c(0)\,\pd T^X(0)
%		- \frac{1}{z}\,T^X(0)\,\pd c(0),
%	\end{aligned}\\
%		T(z)\,j(0)
%		\sim \frac{D}{2z^4}\,c(0)
%			+ \frac{2}{z^2}\,T^X(0)\,c(0)
%			+ \frac{1}{z}\,\pqty{
%				\pd j(0)
%				- T^X(0)\,\pd c(0)
%			}
%	\end{equation}

	\item For $jj$ OPE, we have:
	\begin{gather}
		j = cT^X + j',\quad
		j' \equiv j^{bc}
			+ \frac{3}{2}\,\pd^2 c,\quad
		j^{bc}
		= \frac{1}{2}\normorder{cT^{bc}}
		= \normorder{bc\,\pd c}\,,\\[1ex]
%		
%		j = \frac{1}{2}\,cT^X
%			+ \frac{1}{2}\,\normorder{cT}
%			+ \frac{3}{2}\,\pd^2 c,\\
%
	\begin{aligned}
		j_z j_0
		&\sim \normorder{\Bqty{T^X_z T^X_0}\,c_z c_0}
			+ \normorder{\Bqty{c_z j'_0}\,T^X_z}
			+ \normorder{\Bqty{j'_z c_0}\,T^X_0}
			+ {j'_z j'_0} \\[.5ex]
		&\sim \normorder{\Bqty{T^X_z T^X_0}\,c_z c_0}
			+ \normorder{\Bqty{c_z j^{bc}_0}\,T^X_z}
			+ \normorder{\Bqty{j^{bc}_z c_0}\,T^X_0}
			+ {j'_z j'_0}\,,
	\end{aligned}
	\end{gather}
	From now on, for convenience and clarity, we will use subscripts to denote variable dependence: $c_z = c(z)$. Let's compute this term by term. We have:
	\begin{align}
		\normorder{\Bqty{T^X_z T^X_0}\,c_z c_0}
		&\sim \normorder{\pqty{
			\frac{D}{2z^4}
			+ \frac{2}{z^2}\,{T^X_0}
			+ \frac{1}{z}\,{\pd T^X_0}
		}\pqty{
			z\,\pd c_0
			+ \frac{z^2}{2}\,\pd^2 c_0
			+ \frac{z^3}{6}\,\pd^3 c_0
		} c_0} \notag\\
		&\sim -\pqty{
			\frac{D}{2z^3}\,c\,\pd c_0
			+ \frac{D}{4z^2}\,c\,\pd^2 c_0
			+ \frac{D}{12z}\,c\,\pd^3 c_0
			+ \frac{2}{z}\,\normorder{T^X c\,\pd c_0}
		}, 
		\label{eq:BRST_TTcc_OPE} \\[2ex]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		jc OPE ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		j^{bc}_z c_0
		&\sim \frac{1}{2}\,
			\normorder{cT^{bc}}_{z}\,c_0
		\sim \frac{1}{2}\,c_z \Bqty{
			\normorder{T^{bc}}_{z}\,c_0
		}
		\sim \frac{1}{2}\,c_z \Bqty{
			T_z\,c_0
		} \notag\\
		&\sim -\frac{1}{2}\,\pqty{
			\frac{-1}{z^2}\,c_0
			+ \frac{1}{z}\,\pd c_0
		}\pqty\big{
			c_0 + z\,\pd c_0
		} \sim 0, \\
		j^{bc}_0 c_z
		&\sim 0,
	\end{align}
	\begin{equation}
	\begin{aligned}
		j'_z j'_0
		&\sim j^{bc}_z j^{bc}_0
			+ \frac{3}{2}\,j^{bc}_z\,\pd^2 c_0
			+ \frac{3}{2}\,\pd^2 c_z\,j^{bc}_0 \\
		&\sim \frac{1}{2}\,
			\normorder{cT^{bc}}_{z}\,j^{bc}_0
		+ \frac{3}{2}\,\pqty{
			j^{bc}_z\,\pd^2 c_0
			+ \pd^2 c_z\,j^{bc}_0
		},
	\end{aligned}
	\end{equation}

@@

%	For the first term, we have:
%	\begin{equation}
%	\begin{aligned}
%		\normorder{cT^{bc}}_{z}\,j^{bc}_0
%		&\sim \normorder{\wick{
%			\c1 c T^{bc}_z \c1 j^{bc}_0
%		}} + \normorder{\wick{
%			c \c1 T^{bc}_z \c1 j^{bc}_0
%		}} + \normorder{\wick{
%			\bcontraction[1.1ex]{c}{T}{^{bc}_z}{j}
%			\c1 c T^{bc}_z \c1 j^{bc}_0
%		}} \\[.5ex]
%		&\sim \frac{1}{z}\,(+1)\,\normorder{
%			T^{bc}_z c\,\pd c_0
%		} + \normorder{c_z \Bqty{
%			\eqref{eq:BRST_Tj_OPE_partIII}
%		}} + \frac{1}{z}\,\normorder{\pqty\Big{
%			\Bqty{T^{bc}_z c_0}\,\pd c_0
%			+ (+1)\,
%				c_0\,\Bqty{T^{bc}_z\,\pd c_0}
%		}} \\
%		&\sim \frac{1}{z}\,\normorder{
%			T^{bc} c\,\pd c_0
%		} + \normorder{c_z \Bqty{
%			\eqref{eq:BRST_Tj_OPE_partIII}
%		}} + \frac{1}{z}\,\normorder{\pqty\Big{
%			\Bqty{T^{bc}_z c_0}\,\pd c_0
%			+ c_0\,\Bqty{T^{bc}_z\,\pd c_0}
%		}}
%	\end{aligned}
%	\end{equation}
%	Here we've used the fact that there is only one $b$ in $T^{bc}$, hence all non-singular are accounted for in the above expression. Note again that $c$ is primary; similar to \eqref{eq:BRST_Td2c_OPE}, we have:
%	\begin{equation}
%	\begin{aligned}
%		\normorder{cT^{bc}}_{z}\,j^{bc}_0
%		&\sim \normorder{\pqty{
%			c_0 + z\,\pd c_0
%			+ \frac{z^2}{2}\,\pd^2 c_0
%			+ \frac{z^3}{6}\,\pd^3 c_0
%		} \pqty{
%			\frac{-4}{z^4}\,c_0
%			+ \frac{3}{z^3}\,\pd c_0
%			+ \frac{1}{z^2}\,j^{bc}_0
%			+ \frac{1}{z}\,\pd j^{bc}_0,
%		}} \\
%		&\qquad + \frac{1}{z}\,\pqty{
%			\frac{-1}{z^2}\,c\,\pd c_0
%			+ c_0\cdot\frac{1}{z}\,\pd^2 c_0
%		} \\
%		&\sim \frac{3+4-1}{z^3}\,c\,\pd c_0
%			+ \frac{4/2+1}{z^2}\,c\,\pd^2 c_0
%			+ \frac{4/6}{z}\,c\,\pd^3 c_0 \\
%	\end{aligned}
%	\end{equation}
%	
%	
%	\begin{align}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%		ANOTHER OPE ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		j^{bc}_z\,\pd^2 c_0
%		&\sim \frac{1}{2}\,c_z\,\Bqty{
%			T^{bc}_z\,\pd^2 c_0
%		} \\
%		\sim\eqref{eq:BRST_Td2c_OPE}
%		&\sim \frac{1}{2}\,c_z\,\pqty{
%			\frac{-6}{z^4}\,c_0
%			+ \frac{-2}{z^3}\,\pd c_0
%			+ \frac{1}{z^2}\,\pd^2 c_0
%			+ \frac{1}{z}\,\pd^3 c_0
%		} \\
%		\sim (\textsl{Taylor})
%		&\sim \frac{1}{2}\,\pqty{
%			\frac{6-2}{z^3}\,
%				c_0\,\pd c_0
%			+ \frac{6/2+1}{z^2}\,
%				c_0\,\pd^2 c_0
%			+ \frac{6/6+1}{z}\,
%				c_0\,\pd^3 c_0
%		} \\
%		&\sim \frac{1}{2}\,\pqty{
%			\frac{4}{z^3}\,
%				c_0\,\pd c_0
%			+ \frac{4}{z^2}\,
%				c_0\,\pd^2 c_0
%			+ \frac{2}{z}\,
%				c_0\,\pd^3 c_0
%		} \\[2ex]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%		ANOTHER OPE ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		\pd^2 c_z\,j^{bc}_0
%		&\sim -j^{bc}_0\,\pd^2 c_z \\
%		&\sim - \frac{1}{2}\,c_0\,\Bqty{
%			T^{bc}_0\,\pd^2 c_z
%		} \\
%		\sim\eqref{eq:BRST_Td2c_OPE}
%		&\sim -\frac{1}{2}\,c_0\,\pqty{
%			\frac{-2}{(-z)^3}\,\pd c_z
%			+ \frac{1}{(-z)^2}\,\pd^2 c_z
%			+ \frac{1}{-z}\,\pd^3 c_z
%		} \\
%		&\sim -\frac{1}{2}\,c_0\,\pqty{
%			\frac{2}{z^3}\,\pd c_z
%			+ \frac{1}{z^2}\,\pd^2 c_z
%			+ \frac{-1}{z}\,\pd^3 c_z
%		} \\
%		\sim (\textsl{Taylor})
%		&\sim -\frac{1}{2}\,\pqty{
%			\frac{2}{z^3}\,c_0\,\pd c_0
%			+ \frac{1+2}{z^2}\,c_0\,\pd^2 c_0
%			+ \frac{-1+1+1}{z}\,c_0\,\pd^3 c_0
%		} \\
%		&\sim -\frac{1}{2}\,\pqty{
%			\frac{2}{z^3}\,c_0\,\pd c_0
%			+ \frac{3}{z^2}\,c_0\,\pd^2 c_0
%			+ \frac{1}{z}\,c_0\,\pd^3 c_0
%		} \\[1ex]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		\frac{3}{2}\,\pqty{
%			j^{bc}_z\,\pd^2 c_0
%			+ \pd^2 c_z\,j^{bc}_0
%		} &\sim \frac{3}{4}\,\pqty{
%			\frac{2}{z^3}\,c_0\,\pd c_0
%			+ \frac{1}{z^2}\,c_0\,\pd^2 c_0
%			+ \frac{1}{z}\,c_0\,\pd^3 c_0
%		}
%	\end{align}
